\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{enumitem}

\geometry{margin=2.5cm}

\begin{document}

\textit{[Translation for documentation purposes -- German original is legally binding]}

\vspace{0.5cm}

\textbf{Wolfram Laube}\\
Unterer Stadtplatz 18\\
4780 Schärding, Austria

Phone: +43 664 401 15 21\\
Email: wolfram.laube@blauweiss-edv.at

\vspace{1cm}

\textbf{APOR Unternehmensverwaltung GmbH}\\
Attn: Mag.a Oberndorfer / Mag. Zellinger\\
Insolvency Administrator in proceedings GZ 17 S 35/25 s\\
Regional Court Ried im Innkreis

\vspace{1cm}

\hfill Schärding, \underline{\hspace{4cm}}

\vspace{1cm}

\textbf{Subject: Application for Approval of Employment as IT Service Provider}

Insolvency Proceedings GZ 17 S 35/25 s, Regional Court Ried im Innkreis

\vspace{0.5cm}

Dear Ms. Mag.a Oberndorfer,\\
Dear Mr. Mag. Zellinger,

In connection with the above-referenced insolvency proceedings, I am writing to request your approval for a planned employment activity, which I would like to present to you transparently below.

\section*{1. Background}

Due to the closure of my sole proprietorship Blauweiss EDV e.U., self-employment is currently not possible for me. However, as an IT specialist with over 25 years of professional experience in software architecture, cloud infrastructure, and DevOps, I possess in-demand qualifications that I would like to utilize for the purpose of generating income.

\section*{2. Planned Activity}

I have the opportunity to work as an Independent Contractor for a US-based company:

\begin{itemize}[leftmargin=2cm]
    \item[\textbf{Company:}] Blauweiss-EDV LLC
    \item[\textbf{Registered Office:}] Texas, USA
    \item[\textbf{Registration:}] Texas Secretary of State, File Number 806293404
    \item[\textbf{Members:}] Michael Clement Matejka, Ian Bennett Matejka (both US citizens)
\end{itemize}

\section*{3. Clarification Regarding Ownership Structure}

I wish to expressly emphasize that I \textbf{hold no ownership interest in the aforementioned company and will not acquire any ownership interest during the duration of the insolvency proceedings}. The members are long-standing acquaintances who are willing to engage me as an external service provider.

My role is strictly limited to the provision of IT services in exchange for compensation within the framework of a contractor relationship.

\section*{4. Compensation and Standard of Living}

The compensation from this activity will be structured to enable a modest standard of living, as is appropriate during insolvency proceedings. I am aware that excess income would need to be contributed to the insolvency estate, and I commit to complete transparency toward the insolvency administration.

The specific amount of monthly disbursement can be determined in coordination with you.

\section*{5. Transparency and Documentation}

I am prepared to provide you with all relevant documents, in particular:

\begin{itemize}
    \item The Contractor Agreement between myself and Blauweiss-EDV LLC
    \item The Operating Agreement of the LLC (as proof of my non-ownership)
    \item Monthly statements and payment receipts
    \item Any other documentation you may require
\end{itemize}

\section*{6. Application}

I hereby apply for your approval to commence the described activity as an IT contractor for Blauweiss-EDV LLC. I am available for any questions and would be happy to discuss the details in a personal meeting.

\vspace{1cm}

Sincerely,

\vspace{2cm}

\underline{\hspace{6cm}}\\
Wolfram Laube

\vspace{1cm}

\textbf{Attachments:}
\begin{itemize}
    \item Certificate of Filing of Blauweiss-EDV LLC
    \item Operating Agreement (Draft)
    \item Independent Contractor Agreement (Draft)
\end{itemize}

\end{document}
