\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}

\geometry{margin=2.5cm}

\titleformat{\section}{\large\bfseries}{ARTICLE \Roman{section} -- }{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{Section \thesection.\arabic{subsection} -- }{0em}{}

\begin{document}

\begin{center}
{\Large\textbf{OPERATING AGREEMENT}}\\[0.3cm]
of\\[0.3cm]
{\large\textbf{BLAUWEISS-EDV LLC}}\\[0.3cm]
A Texas Limited Liability Company
\end{center}

\vspace{1cm}

This Operating Agreement (the ``\textbf{Agreement}'') is entered into as of \underline{\hspace{3cm}}, 2025 (the ``\textbf{Effective Date}''), by and among the Members identified herein.

\textbf{WHEREAS}, Blauweiss-EDV LLC (the ``\textbf{Company}'') was formed as a Texas Limited Liability Company on November 6, 2025, pursuant to the filing of a Certificate of Formation with the Texas Secretary of State (File Number 806293404); and

\textbf{WHEREAS}, the Members desire to set forth the terms and conditions governing the operation of the Company and the rights and obligations of the Members;

\textbf{NOW, THEREFORE}, in consideration of the mutual covenants and agreements herein contained, the Members agree as follows:

\section{ORGANIZATION}

\subsection{Name}
The name of the Company is Blauweiss-EDV LLC.

\subsection{Principal Place of Business}
The principal place of business of the Company shall be at such location as may be determined by the Members from time to time. The initial registered office is as stated in the Certificate of Formation.

\subsection{Purpose}
The purpose of the Company is to engage in the business of providing information technology services, including but not limited to software development, cloud architecture, DevOps consulting, artificial intelligence solutions, and any other lawful business activities as determined by the Members.

\subsection{Term}
The Company shall have perpetual existence unless dissolved in accordance with this Agreement or applicable law.

\section{MEMBERS AND MEMBERSHIP INTERESTS}

\subsection{Initial Members}
The initial Members of the Company and their respective Membership Interests are as follows:

\begin{quote}
\textbf{Michael Clement Matejka} -- 50\% Membership Interest\\
106 Stratford St, Houston, TX 77006, USA\\
US Citizen

\textbf{Ian Bennett Matejka} -- 50\% Membership Interest\\
Houston, Texas, USA\\
US Citizen
\end{quote}

\subsection{Admission of Additional Members}
Additional Members may be admitted to the Company upon the unanimous written consent of all existing Members and the execution of an amendment to this Agreement reflecting the admission of such new Member and the adjustment of Membership Interests.

\section{MEMBERSHIP OPTION}

\subsection{Grant of Option}
The Members hereby grant to \textbf{Wolfram Laube} (``\textbf{Optionee}''), an Austrian citizen residing at Unterer Stadtplatz 18, 4780 Schärding, Austria, an option (the ``\textbf{Membership Option}'') to acquire a Membership Interest in the Company, subject to the terms and conditions set forth in this Article III.

\subsection{Exercise Conditions}
The Membership Option may only be exercised upon the satisfaction of the following condition: The conclusion of the insolvency proceedings (Konkursverfahren GZ 17 S 35/25 s) currently pending against the Optionee at the Regional Court Ried im Innkreis, Austria, by way of final and binding court order or decree confirming the termination or discharge of such proceedings.

\subsection{Exercise Procedure}
Upon satisfaction of the Exercise Condition, the Optionee may exercise the Membership Option by delivering written notice to all Members, accompanied by documentation evidencing the conclusion of the insolvency proceedings. Upon valid exercise, the Optionee shall be admitted as a Member, and the Membership Interests shall be adjusted such that each of the three Members holds a 33.33\% Membership Interest (or such other allocation as unanimously agreed by all parties).

\subsection{Exercise Price}
The exercise price for the Membership Option shall be One Dollar (\$1.00), representing consideration for the Optionee's contributions to the Company as an Independent Contractor and in recognition of the Optionee's role in establishing the Company's business relationships and technical capabilities.

\subsection{Option Period}
The Membership Option shall remain exercisable for a period of two (2) years following the satisfaction of the Exercise Condition. If not exercised within such period, the Membership Option shall expire.

\subsection{Contractor Relationship}
Pending exercise of the Membership Option, the Optionee shall provide services to the Company as an Independent Contractor pursuant to a separate Independent Contractor Agreement. Such contractor relationship shall not create any membership rights or obligations prior to valid exercise of the Membership Option.

\section{MANAGEMENT}

\subsection{Member-Managed Company}
The Company shall be managed by its Members. Each Member shall have the authority to bind the Company in the ordinary course of business.

\subsection{Voting}
Except as otherwise provided in this Agreement, decisions requiring Member approval shall be made by a majority vote of the Members based on their Membership Interests. The following matters require unanimous consent of all Members:

\begin{enumerate}[label=(\alph*)]
    \item Admission of new Members
    \item Amendment of this Agreement
    \item Dissolution of the Company
    \item Sale of all or substantially all Company assets
    \item Any transaction involving a conflict of interest
\end{enumerate}

\section{CAPITAL CONTRIBUTIONS AND DISTRIBUTIONS}

\subsection{Initial Capital Contributions}
The initial capital contribution of each Member is as follows:

\begin{quote}
Michael Clement Matejka: \$500.00\\
Ian Bennett Matejka: \$500.00
\end{quote}

\subsection{Distributions}
Distributions of available cash shall be made at such times and in such amounts as determined by the Members, in proportion to their respective Membership Interests, unless otherwise unanimously agreed.

\subsection{Retained Earnings}
The Members may elect to retain earnings within the Company for working capital, investment, or other business purposes. Such retained earnings shall be allocated to the Members' capital accounts in proportion to their Membership Interests.

\section{FUTURE MEMBERSHIP EXPANSION}

\subsection{Anticipated Expansion}
The Members acknowledge that it is contemplated that the Company may admit additional Members in the future, potentially including family members of existing Members or other qualified individuals who may contribute to the Company's business objectives.

\subsection{Dilution and Adjustment}
Upon the admission of any new Member, the Membership Interests of existing Members shall be adjusted pro rata unless the Members unanimously agree to a different allocation. All Members shall execute an amendment to this Agreement reflecting any changes to Membership Interests.

\subsection{Right of First Refusal}
Before any Member may transfer a Membership Interest to a third party, the other Members shall have a right of first refusal to acquire such interest on the same terms and conditions offered by the third party.

\section{DISSOLUTION AND WINDING UP}

The Company shall be dissolved upon the occurrence of any of the following events: (a) the unanimous written consent of all Members; (b) the entry of a decree of judicial dissolution; or (c) any other event causing dissolution under applicable law. Upon dissolution, the Company's affairs shall be wound up in accordance with the Texas Business Organizations Code.

\section{MISCELLANEOUS}

\subsection{Governing Law}
This Agreement shall be governed by and construed in accordance with the laws of the State of Texas, without regard to its conflict of laws principles.

\subsection{Amendments}
This Agreement may be amended only by a written instrument signed by all Members.

\subsection{Entire Agreement}
This Agreement constitutes the entire agreement among the Members with respect to the subject matter hereof and supersedes all prior agreements and understandings.

\subsection{Severability}
If any provision of this Agreement is held to be invalid or unenforceable, the remaining provisions shall continue in full force and effect.

\vspace{1cm}

\textbf{IN WITNESS WHEREOF}, the undersigned Members have executed this Operating Agreement as of the Effective Date first written above.

\vspace{1.5cm}

\textbf{MEMBER:}

\vspace{1.5cm}

\underline{\hspace{8cm}}\\
Michael Clement Matejka\\
Date: \underline{\hspace{4cm}}

\vspace{1.5cm}

\textbf{MEMBER:}

\vspace{1.5cm}

\underline{\hspace{8cm}}\\
Ian Bennett Matejka\\
Date: \underline{\hspace{4cm}}

\vspace{1.5cm}

\textbf{ACKNOWLEDGMENT OF OPTIONEE:}

The undersigned acknowledges receipt of this Operating Agreement and agrees to be bound by the terms of Article III (Membership Option) upon exercise thereof.

\vspace{1.5cm}

\underline{\hspace{8cm}}\\
Wolfram Laube (Optionee)\\
Date: \underline{\hspace{4cm}}

\end{document}
