\documentclass[11pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}

\geometry{margin=2.5cm}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
{\Large\bfseries INDEPENDENT CONTRACTOR AGREEMENT}
\end{center}

\vspace{1em}

This Independent Contractor Agreement (the ``\textbf{Agreement}'') is entered into as of \underline{\hspace{3cm}}, 2025 (the ``\textbf{Effective Date}''), by and between:

\textbf{BLAUWEISS-EDV LLC}, a Texas Limited Liability Company\\
(hereinafter referred to as the ``Company'')

and

\textbf{WOLFRAM LAUBE}\\
Unterer Stadtplatz 18, 4780 Schärding, Austria\\
(hereinafter referred to as the ``Contractor'')

(each a ``Party'' and collectively the ``Parties'')

\section*{RECITALS}

\textbf{WHEREAS}, the Company is engaged in the business of providing information technology services, including software development, cloud architecture, DevOps consulting, and artificial intelligence solutions;

\textbf{WHEREAS}, the Contractor possesses specialized skills and expertise in software architecture, cloud infrastructure, DevOps, and AI/machine learning, with over 25 years of professional experience in the IT industry;

\textbf{WHEREAS}, the Contractor is currently subject to insolvency proceedings (Konkursverfahren GZ 17 S 35/25 s) at the Regional Court Ried im Innkreis, Austria, and wishes to engage in gainful employment in a manner consistent with the requirements of such proceedings;

\textbf{NOW, THEREFORE}, in consideration of the mutual covenants and agreements herein contained, the Parties agree as follows:

\section{ENGAGEMENT AND SERVICES}

\subsection{Engagement}
The Company hereby engages the Contractor, and the Contractor hereby accepts such engagement, to provide information technology services to the Company and its clients on the terms and conditions set forth in this Agreement.

\subsection{Scope of Services}
The Contractor shall provide the following services (the ``Services''): (a) Software architecture design and implementation; (b) Cloud infrastructure planning and deployment (AWS, Azure, GCP); (c) DevOps and CI/CD pipeline development; (d) Kubernetes administration and container orchestration; (e) AI/Machine Learning solution development; (f) Technical documentation and consulting; (g) Such other IT services as may be mutually agreed upon.

\subsection{Performance of Services}
The Contractor shall perform the Services remotely from Austria or such other location as the Contractor may determine.

\section{INDEPENDENT CONTRACTOR STATUS}

\subsection{Independent Contractor Relationship}
The Contractor is an independent contractor and not an employee, partner, agent, or joint venturer of the Company. Nothing in this Agreement shall be construed to create an employment relationship between the Parties.

\subsection{No Authority to Bind}
The Contractor shall have no authority to bind the Company or to enter into any contracts or commitments on behalf of the Company unless expressly authorized in writing.

\subsection{Taxes and Social Contributions}
The Contractor shall be solely responsible for all taxes, social security contributions, and other statutory obligations arising from the compensation received under this Agreement.

\section{COMPENSATION}

\subsection{Modest Living Compensation}
In recognition of the Contractor's current circumstances, including the pending insolvency proceedings, the Parties agree that the Contractor shall receive a fixed monthly compensation sufficient to maintain a modest standard of living appropriate for a person subject to insolvency proceedings under Austrian law. The specific monthly amount shall be determined in consultation with the insolvency administrator (APOR Unternehmensverwaltung GmbH) and shall be documented in a written addendum to this Agreement.

\subsection{Payment Terms}
Payment shall be made by bank transfer to an account designated by the Contractor, payable within fifteen (15) days following the end of each calendar month in which Services were provided.

\subsection{Currency}
All compensation shall be denominated and paid in Euros (EUR).

\subsection{Expenses}
The Company shall reimburse the Contractor for reasonable and pre-approved out-of-pocket expenses incurred in connection with the Services.

\subsection{Accounting}
The Company shall provide the Contractor with monthly statements showing Services rendered and compensation paid. Such statements shall be available for review by the insolvency administrator upon request.

\section{TERM AND TERMINATION}

\subsection{Term}
This Agreement shall commence on the Effective Date and shall continue until terminated by either Party in accordance with this Article.

\subsection{Termination for Convenience}
Either Party may terminate this Agreement at any time upon thirty (30) days' prior written notice to the other Party.

\subsection{Termination for Cause}
Either Party may terminate this Agreement immediately upon written notice if the other Party materially breaches any provision of this Agreement and fails to cure such breach within fifteen (15) days after receiving written notice thereof.

\subsection{Effect of Termination}
Upon termination: (a) the Company shall pay the Contractor all compensation earned through the date of termination; (b) the Contractor shall deliver to the Company all work product and materials; and (c) the provisions of Articles 5, 6, and 7 shall survive termination.

\section{CONFIDENTIALITY}

The Contractor agrees to maintain the confidentiality of all proprietary and confidential information of the Company and its clients. This obligation shall survive termination for five (5) years.

\section{INTELLECTUAL PROPERTY}

All work product, inventions, and intellectual property created by the Contractor in the course of providing Services shall be the sole property of the Company. The Contractor hereby assigns all rights in such work product to the Company.

\section{REPRESENTATIONS AND WARRANTIES}

\subsection{Contractor's Representations}
The Contractor represents and warrants that: (a) The Contractor has disclosed the pending insolvency proceedings; (b) The Contractor will obtain required approvals from the insolvency administrator; (c) The Contractor has the legal capacity to enter into this Agreement.

\subsection{Company's Representations}
The Company represents and warrants that it has the authority to enter into this Agreement.

\section{MISCELLANEOUS}

\subsection{Governing Law}
This Agreement shall be governed by the laws of the State of Texas.

\subsection{Amendments}
This Agreement may be amended only by a written instrument signed by both Parties.

\subsection{Entire Agreement}
This Agreement constitutes the entire agreement between the Parties.

\subsection{Severability}
If any provision is held invalid, the remaining provisions shall continue in full force.

\vspace{2em}
\section*{SIGNATURES}

\textbf{IN WITNESS WHEREOF}, the Parties have executed this Agreement as of the Effective Date.

\vspace{2em}
\textbf{BLAUWEISS-EDV LLC}

\vspace{1em}
By: \underline{\hspace{6cm}}\\
Name: Michael Clement Matejka\\
Title: Managing Member\\
Date: \underline{\hspace{4cm}}

\vspace{2em}
\textbf{CONTRACTOR}

\vspace{1em}
\underline{\hspace{6cm}}\\
Wolfram Laube\\
Date: \underline{\hspace{4cm}}

\end{document}
